Approaching Optimal Duplicate Detection in a Sliding Window

### 2020-05-10 article_content.tex
fixes

\begin{restatable}{thm}{asymptoticSaturation}\label{thm:asymptoticSaturation}
	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $EP_n = \FP_n + \FN_n$ satisfies
$
	EP_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
$
	for any $n > M$.
\end{restatable}
In particular, the asymptotic error probability $EP_\infty$ satisfies 
$
	EP_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|.
$

>>>>

\begin{restatable}{thm}{asymptoticSaturation}\label{thm:asymptoticSaturation}
	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $EP_n = \FP_n + \FN_n$ satisfies
$
	EP_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
$
	for any $n > M$.
\end{restatable}
In particular, the asymptotic error probability $EP  _\infty$ satisfies 
$
	EP_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|.
$
